---
title: "OSC survey results 17.10.2022"
format: html
editor: visual
---

```{r}
#| echo: false
#| include: false

library(stringr)
library(tidyverse)

```

## Descriptive statistics

```{r}
#| echo: false
data <- read.csv("OSC.csv", header = TRUE)
data <- data[data$ended != "",]
data <- data[data$freecareer != "thank the formr monkey",]
```

Total number of participant in the OSC survey: **`r nrow(data)`**

## Survey Resuts

### Participants

#### OSC affiliation

```{r}
#| echo: false
table(data$affiliation)
```

#### Organisation location

```{r}
#| echo: false
table(data$organisation)
```

#### Discipline

```{r}
#| echo: false
table(data$discipline)
```

#### Career stage

```{r}
#| echo: false
table(data$career)
table(data$freecareer[data$freecareer != ""])

```

#### Subset for OSC members only?

```{r}
#| echo: false
# subset for official LMU OSC members
#data <- data[data$affiliation == "Yes",]

if (nrow(data) == nrow(data[data$affiliation == "Yes",])) {"Yes"} else {"No"}
```

### Activities

'What activities would you like the OSC community to undertake?'

```{r}
#| echo: false

data$activities_Training <- grepl("training", data$activities, fixed = TRUE)
data$activities_OSC_instructor_training <- grepl("instructor", data$activities, fixed = TRUE)
data$activities_Branded_instructor_training <- grepl("carpentries", data$activities, fixed = TRUE)
data$activities_Seminar <- grepl("seminar", data$activities, fixed = TRUE)
data$activities_Community_calls <- grepl("community calls", data$activities, fixed = TRUE)
data$activities_LMU_chat <- grepl("LMU chat", data$activities, fixed = TRUE)
data$activities_Meta_research <- grepl("meta research", data$activities, fixed = TRUE)
data$activities_Advocacy <- grepl("advocacy", data$activities, fixed = TRUE)
data$activities_Hackathon <- grepl("hackathon", data$activities, fixed = TRUE)


data_activities <- data[, grepl(pattern="activities_", x=colnames(data), fixed = TRUE)]

activities_to_plot <- colSums(data_activities)
names(activities_to_plot) <- str_remove(names(activities_to_plot), "activities_")

activities_to_plot <- sort(activities_to_plot, decreasing = FALSE)

par(mar = c(4,12,4,4))
barplot(activities_to_plot, horiz = TRUE, las = 1, xlim = c(0,20))


```

#### Other activities

```{r}
#| echo: false
table(data$freeactivities[data$freeactivities != ""])
```

### Topics

'Which topics would you be interested to hear about in talks/workshops/seminars?'

```{r}
#| echo: false
data$topics_QRP <- grepl("QRP", data$topics, fixed = TRUE)
data$topics_Preregistration <- grepl("prereg", data$topics, fixed = TRUE)
data$topics_Stats <- grepl("stats", data$topics, fixed = TRUE)
data$topics_Reproducibility <- grepl("reproducibility", data$topics, fixed = TRUE)
data$topics_RDM <- grepl("RDM", data$topics, fixed = TRUE)
data$topics_FAIR <- grepl("FAIR", data$topics, fixed = TRUE)
data$topics_Reporting_guidelines <- grepl("reporting", data$topics, fixed = TRUE)
data$topics_OA <- grepl("OA", data$topics, fixed = TRUE)
data$topics_Copyrights <- grepl("copyrights", data$topics, fixed = TRUE)
data$topics_Meta_research <- grepl("metaresearch", data$topics, fixed = TRUE)
data$topics_Incentives_Policies <- grepl("policies", data$topics, fixed = TRUE)
data$topics_Research_culture <- grepl("culture", data$topics, fixed = TRUE)
data$topics_discipline <- grepl("discipline", data$topics, fixed = TRUE)


data_topics <- data[, grepl(pattern="topics_", x=colnames(data), fixed = TRUE)]

topics_to_plot <- colSums(data_topics)
names(topics_to_plot) <- str_remove(names(topics_to_plot), "topics_")

topics_to_plot <- sort(topics_to_plot, decreasing = FALSE)

par(mar=c(4,10,4,4))
barplot(topics_to_plot, horiz = TRUE, las = 1, xlim = c(0,20))


```

#### Other topics and specific discipline

```{r}
#| echo: false

table(data$specificdiscipline[data$specificdiscipline != ""])
table(data$freetopic[data$freetopic != ""])
```

### Duration

'What length of events would you consider joining?'

```{r}
#| echo: false

data$duration_max_1h <- grepl("1h", data$duration, fixed = TRUE)
data$duration_2_3h <- grepl("2-3h", data$duration, fixed = TRUE)
data$duration_halfday <- grepl("half-day", data$duration, fixed = TRUE)
data$duration_multidays <- grepl("multi-day", data$duration, fixed = TRUE)

data_duration <- data[, grepl(pattern="duration_", x=colnames(data), fixed = TRUE)]

duration_to_plot <- colSums(data_duration)
names(duration_to_plot) <- str_remove(names(duration_to_plot), "duration_")

duration_to_plot <- sort(duration_to_plot, decreasing = FALSE)

par(mar=c(4,10,4,4))
barplot(duration_to_plot, horiz = TRUE, las = 1, xlim = c(0,20))


```

### Participation

'In what way would you prefer to participate in the OSIP community?'

```{r}
#| echo: false

data$participation_Attend_Seminar <- grepl("attend seminar", data$participation, fixed = TRUE)
data$participation_Lead_Seminar <- grepl("lead seminar", data$participation, fixed = TRUE)
data$participation_Attend_Workshop <- grepl("attend workshop", data$participation, fixed = TRUE)
data$participation_Lead_Workshop <- grepl("lead workshop", data$participation, fixed = TRUE)
data$participation_Attend_community_call <- grepl("attend comm call", data$participation, fixed = TRUE)
data$participation_Present_at_community_call <- grepl("present comm call", data$participation, fixed = TRUE)
data$participation_Attend_JC <- grepl("attend JC", data$participation, fixed = TRUE)
data$participation_Facilitate_JC <- grepl("host JC", data$participation, fixed = TRUE)
data$participation_Attend_hachathon <- grepl("attend hackathon", data$participation, fixed = TRUE)
data$participation_Facilitate_hachathon <- grepl("facilitate hackathon", data$participation, fixed = TRUE)
data$participation_Attend_networking_event <- grepl("attend networking event", data$participation, fixed = TRUE)
data$participation_Organise_networking_event <- grepl("organize networking event", data$participation, fixed = TRUE)
data$participation_Join_discussion_on_LMU_chat <- grepl("LMU chat", data$participation, fixed = TRUE)
data$participation_Read_newsletter <- grepl("read newsletter", data$participation, fixed = TRUE)
data$participation_Contribute_to_newsletter <- grepl("contribute newsletter", data$participation, fixed = TRUE)
data$participation_Be_a_contact_person <- grepl("contact person", data$participation, fixed = TRUE)

data_participation <- data[, grepl(pattern="participation_", x=colnames(data), fixed = TRUE)]

participation_to_plot <- colSums(data_participation)
names(participation_to_plot) <- str_remove(names(participation_to_plot), "participation_")

participation_to_plot <- sort(participation_to_plot, decreasing = FALSE)

par(mar=c(4,15,4,4))
barplot(participation_to_plot, horiz = TRUE, las = 1, xlim = c(0,20))


```

#### Other participation

```{r}
#| echo: false
table(data$freeparticipation[data$freeparticipation != ""])
```

### Inclusion

'If you have any comment(s) about what would help you feel comfortable contributing (e.g., language, online vs. in-person events, synchronous vs asynchronous contributions), please indicate them here:'

```{r}
#| echo: false
data$inclusion[data$inclusion != "" & data$inclusion != "nope" & data$inclusion != "/" & data$inclusion != "nothing" & data$inclusion != "." & data$inclusion != "x" & data$inclusion != "leer" & data$inclusion != " " & data$inclusion != "-" & data$inclusion != "not sure" & data$inclusion != "--"]
```

### Comments

'If you have any other suggestions, please indicate them here:'

```{r}
#| echo: false
data$comment[data$comment != "" & data$comment != "nope" & data$comment != "/" & data$comment != "nothing" & data$comment != "." & data$comment != "x" & data$comment != "leer" & data$comment != " " & data$comment != "-" & data$comment != "not sure" & data$comment != "--" & data$comment != "No." & data$comment != "No" & data$comment != "nope :)" & !is.na(data$comment) & data$comment != "No other comments." & data$comment != "no" & data$comment != "nein"]
```
